---
title: "engression_worksheet"
author: "Philip Boustani"
date: "2024-03-24"
output: html_document
---

# Setup Rmarkdown

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# install and loed packages

```{r}
# List of required packages
packages <- c(
  "engression",
  "CondIndTests", 
  "lawstat", # For levene.test
  "stats", # For ks.test, wilcox.test
  "mgcv", # for fitting GAMs
  "nonlinearICP",
  "readtext", # loading csv files
  # "utils", # progress bar 
  "foreach",
  "doSNOW",  # parallel processing with progress bar 
  "data.tree", # to create tree structures from hierarchical data
  "quantregForest", # quantile regression forest
  # "InvariantCausalPrediction",
  # "distributionsrd",
  "torch"
)

# First, installing packages which are not yet installed and then loading all of them
load_packages <- function(packages){
  for (pkg in packages) {
    if(!require(pkg, character.only = TRUE)){
      install.packages(pkg, character.only = TRUE);
      library(pkg, character.only = TRUE)
    }
  }
}

# loading packages
load_packages(packages)
```

# load all required source files

```{r}
# List of required source files
files <- c(
)

# if applicable, specify entire folders to be loaded
folders <- c(
  "gaussianEngression",
  "engression_supplementary",
  "external_modified"
)

# Detect working directory and load all files 
load_files <- function(files, folders, directory){
  
  paths <- c(
    file.path(directory, files),
    file.path(directory, list.files(folders, full.names = TRUE))
  )
  
  for (path in paths) {
    source(path)
  }
}

# loading directory  
directory <- getwd()
load_files(files, folders, directory)
```



# PART 1 -----------------------------------------------------------------------
# INV. RESIDUAL DISTRIBUTION TEST 

# Simulate data and compute p-vals.

```{r}
n <- 2000 # \in (100, 200, 500, 2000, 5000)
SimRep <- 100
method <- "GAM"
test <- "InvResDist"

# Set up parallel computing
cluster <- makeSOCKcluster(3)
registerDoSNOW(cluster)

# setting up progress bar
pb <- txtProgressBar(max=SimRep, style=3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress=progress)

# Starting parallel processing unit
foreach(rep = 1:SimRep,
        .errorhandling = 'pass',
        .combine=rbind,
        .options.snow = opts ) %dopar% { # for(rep in 1:SimRep)
          
  # loading all packages into cores
  load_packages(packages)
  # loading source files into cores
  load_files(files, folders, directory) 

  # Setting up framework for error message printing
  tryCatch(
  # Start Computations
    {

  Simulation <- gen_sample(n = n, d = d, dag = dag,
                  signs = dag_signs, betas = dag_coefs, target = "random",
                  verbose = FALSE , preSI = TRUE)

  target <- Simulation$statistics[2]
  S_sets <- obtain_S(target, d)
  pvals <- rep(NA, length(S_sets))
  names(pvals) <- paste("pvSet",1:length(S_sets),sep = "_")

  for (k in 1:length(S_sets)) {

    S_k <- S_sets[[k]]

    pvals[k] <- InvResDisTest(
      Y = Simulation$sample[,target], 
      E = as.factor(Simulation$sample[,"E"]),
      X = Simulation$sample[,S_k],
      alpha = 0.05,
      verbose = FALSE, fitmodel = method,
      test = leveneAndWilcoxResidualDistributions, colNameNoSmooth = NULL,
      mtry = sqrt(NCOL(X)), ntree = 100, nodesize = 5, maxnodes = NULL,
      noise_dim = 5,
      hidden_dim = 100,
      num_layer = 3,
      num_epochs = 30, # default set to 1000
      silent = TRUE,
      returnModel = FALSE
    )$pvalue
  }

  record_stats( c(Simulation$statistics, round(pvals,4)),
               title = paste(test, "SimRep_preSI", method, sep = "_") )
  record_stats(Simulation$documentation,
               title = paste(test, "IntDoc_preSI", method, sep = "_") )
  

  # end computations and start error report 
    }, error = function(e) {

      # printing error if occurred
      record_stats( c(Simulation$statistics, conditionMessage(e)),
               title =  paste(test, "ErrorReport_preSI", method, sep = "_") )
    }
  # ending tryCatch
  ) 
# ending parallel processing 
}


close(pb)
stopCluster(cluster)
```



# ---------------------------------------------------------------------------- #
# PART 2
# INV. RESIDUAL DISTRIBUTION TEST 
# ---------------------------------------------------------------------------- #


```{r}
# Set up simulation settings
n <- 50 # \in (100, 200, 500, 2000, 5000)
SimRep <- 10
num_epochs <- 10
test <- "InvResDisTest_preSI"

# Set up parallel computing
cluster <- makeSOCKcluster(3)
registerDoSNOW(cluster)

# setting up progress bar
pb <- txtProgressBar(max=SimRep, style=3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress=progress)

# Starting parallel processing unit
foreach(rep = 1:SimRep,
        .errorhandling = 'pass',
        .combine=rbind,
        .options.snow = opts ) %dopar% { # for(rep in 1:SimRep)
          
  # loading all packages into cores
  load_packages(packages)
  # loading source files into cores
  load_files(files, folders, directory) 

  # Setting up framework for error message printing
  tryCatch(
  # Start Computations
    {
  
      Simulation <- gen_sample(n = n, d = d, dag = dag,
                  signs = dag_signs, betas = dag_coefs, target = "random",
                  verbose = FALSE , preSI = TRUE)

      target <- Simulation$statistics[2]
      S_sets <- obtain_S(target, d)
      pvals <- rep(NA, length(S_sets))
      names(pvals) <- paste("pvSet",1:length(S_sets),sep = "_")
      
      
      method <- "GSIengression" # \in (GAM, engression, GSIengression)
    
      for (k in 1:length(S_sets)) {
    
        S_k <- S_sets[[k]]
        Xinput <- as.matrix(Simulation$sample[,S_k])
        colnames(Xinput) <- S_k
          
        # InvResDisTest
        result <- InvResDisTest(
          Y = Simulation$sample[,target],
          E = as.factor(Simulation$sample[,"E"]),
          X = Xinput,
          alpha = 0.05,
          verbose = FALSE, fitmodel = method,
          test = leveneAndWilcoxResidualDistributions, colNameNoSmooth = NULL,
          mtry = sqrt(NCOL(Xinput)), ntree = 100, nodesize = 5, maxnodes = NULL,
          noise_dim = 5,
          hidden_dim = 100,
          num_layer = 3,
          num_epochs = num_epochs, # default set to 1000
          silent = TRUE,
          returnModel = FALSE
        )
        
        pvals[k] <- result$pvalue
        
        record_stats(c(ID = Simulation$statistics[1], set = k, pvalue = round(pvals[k],4), 
                       result$beta_hat, result$sd_hat),
                   title = paste(test, "BetaDoc", method, sep = "_") )
      }
      
      # record computations
      record_stats( c(Simulation$statistics, round(pvals,4)),
                   title = paste(test, "SimRep", method, sep = "_") )
      record_stats(Simulation$documentation,
                   title = paste(test, "IntDoc", method, sep = "_") )

        
      method <- "GAM" # \in (GAM, engression, GSIengression)
      
      for (k in 1:length(S_sets)) {
    
        S_k <- S_sets[[k]]
        Xinput <- as.matrix(Simulation$sample[,S_k])
        colnames(Xinput) <- S_k
        
        # InvResDisTest
        result <- InvResDisTest(
          Y = Simulation$sample[,target],
          E = as.factor(Simulation$sample[,"E"]),
          X = Xinput,
          alpha = 0.05,
          verbose = FALSE, fitmodel = method,
          test = leveneAndWilcoxResidualDistributions, colNameNoSmooth = NULL,
          mtry = sqrt(NCOL(Xinput)), ntree = 100, nodesize = 5, maxnodes = NULL,
          noise_dim = 5,
          hidden_dim = 100,
          num_layer = 3,
          num_epochs = num_epochs, # default set to 1000
          silent = TRUE,
          returnModel = FALSE
        )
        
        pvals[k] <- result$pvalue
      }
      
      # record computations
      record_stats( c(Simulation$statistics, round(pvals,4)),
                   title = paste(test, "SimRep", method, sep = "_") )
      record_stats(Simulation$documentation,
                   title = paste(test, "IntDoc", method, sep = "_") )
      
      
    # end computations and start error report 
    }, error = function(e) {

      # printing error if occurred
      record_stats( c(Simulation$statistics, conditionMessage(e)),
               title =  paste(test, "ErrorReport", method, sep = "_") )
    }
  # ending tryCatch
  ) 
# ending parallel processing 
}


close(pb)
stopCluster(cluster)
```



# ---------------------------------------------------------------------------- #
# Invariant Conditional Quantile Prediction
# ---------------------------------------------------------------------------- #


```{r}
# Set up simulation settings
n <- 5000 # \in (100, 200, 500, 2000, 5000)
num_epochs <- 100
SimRep <- 53
test <- "InvConQuanPred_preSI"

# Set up parallel computing
cluster <- makeSOCKcluster(3)
registerDoSNOW(cluster)

# setting up progress bar
pb <- txtProgressBar(max=SimRep, style=3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress=progress)

# Starting parallel processing unit
foreach(rep = 1:SimRep,
        .errorhandling = 'pass',
        .combine=rbind,
        .options.snow = opts ) %dopar% {
          
  # loading all packages into cores
  load_packages(packages)
  # loading source files into cores
  load_files(files, folders, directory) 

  # Setting up framework for error message printing
  tryCatch(
  # Start Computations
    {
      method <- "SIE"
      
      Simulation <- gen_sample(n = n, d = d, dag = dag,
                  signs = dag_signs, betas = dag_coefs, target = "random",
                  verbose = FALSE , preSI = TRUE)

      target <- Simulation$statistics[2]
      S_sets <- obtain_S(target, d)
      pvals <- rep(NA, length(S_sets))
      names(pvals) <- paste("pvSet",1:length(S_sets),sep = "_")
    
      for (k in 1:length(S_sets)) {
    
        S_k <- S_sets[[k]]
        Xinput <- as.matrix(Simulation$sample[,S_k])
        colnames(Xinput) <- S_k
        
        result <- InvariantConditionalQuantilePrediction(
                        Y = Simulation$sample[,target],
                        E = as.factor(Simulation$sample[,"E"]),
                        X = Xinput,
                        fitmodel = method, # also: RF, engression
                        alpha = 0.05,
                        verbose = FALSE,
                        test = fishersTestExceedance,
                        mtry = sqrt(NCOL(Xinput)),
                        ntree = 100,
                        nodesize = 5,
                        maxnodes = NULL,
                        quantiles = c(0.1, 0.5, 0.9),
                        returnModel = FALSE, 
                        noise_dim = 5, # engression specifications
                        hidden_dim = 100,
                        num_layer = 3,
                        dropout = 0.05,
                        batch_norm = TRUE,
                        num_epochs = num_epochs,
                        lr = 10^(-3),
                        beta = 1,
                        silent = TRUE,
                        standardize = TRUE)
        
        pvals[k] <- result$pvalue
        
        record_stats(c(ID = Simulation$statistics[1], set = k, pvalue = round(pvals[k],4), 
                       result$beta_hat, result$sd_hat),
                   title = paste(test, "BetaDoc", method, sep = "_") )
      }
      
      # record computations
      record_stats( c(Simulation$statistics, round(pvals,4)),
                   title = paste(test, "SimRep", method, sep = "_") )
      record_stats(Simulation$documentation,
                   title = paste(test, "IntDoc", method, sep = "_") )

      method <- "RF"
      
      for (k in 1:length(S_sets)) {
    
        S_k <- S_sets[[k]]
        Xinput <- as.matrix(Simulation$sample[,S_k])
        colnames(Xinput) <- S_k
        
        result <- InvariantConditionalQuantilePrediction(
                        Y = Simulation$sample[,target],
                        E = as.factor(Simulation$sample[,"E"]),
                        X = Xinput,
                        fitmodel = method, # also: engression, SIE
                        alpha = 0.05,
                        verbose = FALSE,
                        test = fishersTestExceedance,
                        mtry = sqrt(NCOL(Xinput)),
                        ntree = 100,
                        nodesize = 5,
                        maxnodes = NULL,
                        quantiles = c(0.1, 0.5, 0.9),
                        returnModel = FALSE, 
                        noise_dim = 5, # engression specifications
                        hidden_dim = 100,
                        num_layer = 3,
                        dropout = 0.05,
                        batch_norm = TRUE,
                        num_epochs = num_epochs,
                        lr = 10^(-3),
                        beta = 1,
                        silent = TRUE,
                        standardize = TRUE)
        
        pvals[k] <- result$pvalue
      }

      # record computations
      record_stats( c(Simulation$statistics, round(pvals,4)),
                   title = paste(test, "SimRep", method, sep = "_") )
      record_stats(Simulation$documentation,
                   title = paste(test, "IntDoc", method, sep = "_") )
      
    # end computations and start error report 
    }, error = function(e) {

      # printing error if occurred
      record_stats( c(Simulation$statistics, conditionMessage(e)),
               title =  paste(test, "ErrorReport", method, sep = "_") )
    }
  # ending tryCatch
  ) 
# ending parallel processing 
}


close(pb)
stopCluster(cluster)
```




```{r}
# Set up simulation settings
n <- 100 # \in (100, 200, 500, 2000, 5000)
num_epochs <- 100
SimRep <- 50
test <- "Monotone_preSI_QPT_RDT"

# Set up parallel computing
cluster <- makeSOCKcluster(3)
registerDoSNOW(cluster)

# setting up progress bar
pb <- txtProgressBar(max=SimRep, style=3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress=progress)

# Starting parallel processing unit
foreach(rep = 1:SimRep,
        .errorhandling = 'pass',
        .combine=rbind,
        .options.snow = opts ) %dopar% {
          
  # loading all packages into cores
  load_packages(packages)
  # loading source files into cores
  load_files(files, folders, directory) 

  # Setting up framework for error message printing
  tryCatch(
  # Start Computations
    {
      method <- "engression"
      
      Simulation <- gen_sample(n = n, d = d, dag = dag,
                  signs = dag_signs, betas = dag_coefs, target = "random",
                  verbose = FALSE , preSI = TRUE, monotone_fun = TRUE)

      target <- Simulation$statistics[2]
      S_sets <- obtain_S(target, d)
      pvals <- rep(NA, length(S_sets))
      names(pvals) <- paste("pvSet",1:length(S_sets),sep = "_")
    
      for (k in 1:length(S_sets)) {
    
        S_k <- S_sets[[k]]
        Xinput <- as.matrix(Simulation$sample[,S_k])
        colnames(Xinput) <- S_k
        
        result <- InvariantConditionalQuantilePrediction(
                        Y = Simulation$sample[,target],
                        E = as.factor(Simulation$sample[,"E"]),
                        X = Xinput,
                        fitmodel = method, # also: RF, engression
                        alpha = 0.05,
                        verbose = FALSE,
                        test = fishersTestExceedance,
                        mtry = sqrt(NCOL(Xinput)),
                        ntree = 100,
                        nodesize = 5,
                        maxnodes = NULL,
                        quantiles = c(0.1, 0.5, 0.9),
                        returnModel = FALSE, 
                        noise_dim = 5, # engression specifications
                        hidden_dim = 100,
                        num_layer = 3,
                        dropout = 0.05,
                        batch_norm = TRUE,
                        num_epochs = num_epochs,
                        lr = 10^(-3),
                        beta = 1,
                        silent = TRUE,
                        standardize = TRUE)
        
        pvals[k] <- result$pvalue
        
        # record_stats(c(ID = Simulation$statistics[1], set = k, pvalue = round(pvals[k],4), 
        #                result$beta_hat, result$sd_hat),
        #            title = paste(test, "BetaDoc", method, sep = "_") )
      }
      
      # record computations
      record_stats( c(Simulation$statistics, round(pvals,4)),
                   title = paste(test, "SimRep", method, sep = "_") )
      record_stats(Simulation$documentation,
                   title = paste(test, "IntDoc", method, sep = "_") )

      method <- "GAM" # \in (GAM, engression, GSIengression)
      
      for (k in 1:length(S_sets)) {
    
        S_k <- S_sets[[k]]
        Xinput <- as.matrix(Simulation$sample[,S_k])
        colnames(Xinput) <- S_k
        
        # InvResDisTest
        result <- InvResDisTest(
          Y = Simulation$sample[,target],
          E = as.factor(Simulation$sample[,"E"]),
          X = Xinput,
          alpha = 0.05,
          verbose = FALSE, fitmodel = method,
          test = leveneAndWilcoxResidualDistributions, colNameNoSmooth = NULL,
          mtry = sqrt(NCOL(Xinput)), ntree = 100, nodesize = 5, maxnodes = NULL,
          noise_dim = 5,
          hidden_dim = 100,
          num_layer = 3,
          num_epochs = num_epochs, # default set to 1000
          silent = TRUE,
          returnModel = FALSE
        )
        
        pvals[k] <- result$pvalue
      }
      
      # record computations
      record_stats( c(Simulation$statistics, round(pvals,4)),
                   title = paste(test, "SimRep", method, sep = "_") )
      record_stats(Simulation$documentation,
                   title = paste(test, "IntDoc", method, sep = "_") )
      
    # end computations and start error report 
    }, error = function(e) {

      # printing error if occurred
      record_stats( c(Simulation$statistics, conditionMessage(e)),
               title =  paste(test, "ErrorReport", method, sep = "_") )
    }
  # ending tryCatch
  ) 
# ending parallel processing 
}


close(pb)
stopCluster(cluster)
```





# ---------------------------------------------------------------------------- #
# LINEAR ICP
# ---------------------------------------------------------------------------- #


```{r}
n <- 5000 # \in (100, 200, 500, 2000, 5000)
SimRep <- 100
test <- "InvResDist"

# Set up parallel computing
cluster <- makeSOCKcluster(3)
registerDoSNOW(cluster)

# setting up progress bar
pb <- txtProgressBar(max=SimRep, style=3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress=progress)

# Starting parallel processing unit
foreach(rep = 1:SimRep,
        .errorhandling = 'pass',
        .combine=rbind,
        .options.snow = opts ) %dopar% {
          
  # loading all packages into cores
  load_packages(packages)
  # loading source files into cores
  load_files(files, folders, directory) 

  # Setting up framework for error message printing
  tryCatch(
  # Start Computations
    {
      method <- "linearICP"
      
      Simulation <- gen_sample(n = n, d = d, dag = dag,
                  signs = dag_signs, betas = dag_coefs, target = "random",
                  verbose = FALSE , preSI = TRUE, monotone_fun = TRUE)

      target <- Simulation$statistics[2]
      S_sets <- obtain_S(target, d)
      pvals <- rep(NA, length(S_sets))
      names(pvals) <- paste("pvSet",1:length(S_sets),sep = "_")
      
      Xinput <- as.matrix(Simulation$sample[,!(colnames(Simulation$sample) %in% c(target, "E"))])
      
      for (k in 1:length(S_sets)) {
    
        S_k <- S_sets[[k]]
        Xinput <- as.matrix(Simulation$sample[,S_k])
        colnames(Xinput) <- S_k
        
        lmfit <- lm(Simulation$sample[,target] ~ Xinput)
        
        pvals[k] <- round(leveneAndWilcoxResidualDistributions(Y = Simulation$sample[,target],  
                                                           predicted = lmfit$fitted.values, 
                                                           E = as.factor(Simulation$sample[,"E"]), 
                                                           verbose=FALSE)$pvalue,4)
        
      }
      
      # record computations
      record_stats( c(Simulation$statistics, pvals),
                   title = paste(test, "SimRep", method, sep = "_") )
      record_stats(Simulation$documentation,
                   title = paste(test, "IntDoc", method, sep = "_") )

  

    # end computations and start error report 
    }, error = function(e) {

      # printing error if occurred
      record_stats( c(Simulation$statistics, conditionMessage(e)),
               title =  paste(test, "ErrorReport", method, sep = "_") )
    }
  # ending tryCatch
  ) 
# ending parallel processing 
}


close(pb)
stopCluster(cluster)
```





# ---------------------------------------------------------------------------- #
# RANDOM
# ---------------------------------------------------------------------------- #


```{r}
n <- 5000 # \in (100, 200, 500, 2000, 5000)
SimRep <- 500
test <- "random"
method <- "random"

# Set up parallel computing
cluster <- makeSOCKcluster(3)
registerDoSNOW(cluster)

# setting up progress bar
pb <- txtProgressBar(max=SimRep, style=3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress=progress)

# Starting parallel processing unit
# foreach(rep = 1:SimRep,
#         .errorhandling = 'pass',
#         .combine=rbind,
#         .options.snow = opts ) %dopar% {
#           
#   # loading all packages into cores
#   load_packages(packages)
#   # loading source files into cores
#   load_files(files, folders, directory) 

for (rep in 1:SimRep) {
  # Setting up framework for error message printing
  tryCatch(
  # Start Computations
    {
      Simulation <- gen_sample(n = n, d = d, dag = dag,
                  signs = dag_signs, betas = dag_coefs, target = "random",
                  verbose = FALSE , preSI = TRUE, monotone_fun = TRUE)
      
  # target_id <- sample(1:d, 1)
  # target <- paste("Z", target_id, sep = "_")
  
  target <- Simulation$statistics[2]
  S_sets <- obtain_S(target, d)
  pvals <- rep(0, length(S_sets))
  
  target_id <- as.numeric(gsub("[^0-9]", "", target))

  
  emptyset <- rbinom(1,1,0.95)
  
  sample_vec <- 1:31
  sample_vec <- sample_vec[sample_vec != target_id] 
  
  if(!emptyset){
    pvals[sample(x = sample_vec,size = 1)] <- 1
  }
  
  names(pvals) <- paste("pvSet",1:length(S_sets),sep = "_")

      
  record_stats( c(Simulation$statistics, pvals),
                 title = paste(test, "SimRep", method, sep = "_") )



    # end computations and start error report 
    }, error = function(e) {

      # printing error if occurred
      record_stats( c(Simulation$statistics, conditionMessage(e)),
               title =  paste(test, "ErrorReport", method, sep = "_") )
    }
  # ending tryCatch
  ) 
# ending parallel processing 
}


close(pb)
stopCluster(cluster)
```














# ---------------------------------------------------------------------------- #
# PART 3
# Compute JACCARD similarity and FWER
# ---------------------------------------------------------------------------- #


```{r}
directory <- getwd()
method <- "SIengressionQPT"
# method <- "SimRep_GSIengression"

# Tests: 
# 1) InvResDisTest_SimRep
# 2) InvConQuanPred_SimRep
# 3) InvResDisTest_preSI
# 3) InvConQuanPred_preSI

# title <- paste("simulation_documentation/InvResDisTest_SimRep", method, sep = "_")
title <- paste("InvConQuanPred_preSI", method, sep = "_")
impdir = directory
fileform = "csv"
delim = ";"
filename <- paste(impdir, "/", title, ".", fileform, sep = "")
```


```{r}
# Monotone_preSI_QPT_RDT_SimRep_engression.csv
statistics <- read.csv("random_SimRep_random.csv", 
                       header = TRUE, sep = ";", encoding="UTF-8")
pvals <- statistics[ , grepl("pvSet_" , names( statistics ) ) ]
```


```{r}
# Define a function to clean and convert the values
clean_numeric <- function(x) {
  x <- gsub(",", ".", x)  # Replace commas with periods
  return(as.numeric(x))   # Convert to numeric
}
pvals <- as.data.frame(lapply(pvals, function(col) sapply(col, clean_numeric)))

# clean data from missing rows
NArows <- which(apply(pvals, 1, function(row) any(is.na(row))))
pvals <- pvals[-NArows,]
statistics <- statistics[-NArows,]
```


```{r}
verbose <- FALSE 
nvec <- nrow(pvals)
AbsIntSetVec <- numeric(nvec)
AbsUnSetVec <- numeric(nvec)
S_in_PA <- numeric(nvec)
int_set_vec <- character(nvec)

for (Sim in 1:nvec) {
  
  if (verbose) cat("\n Sim:",Sim)
  # extract target of the Simulation
  target <- statistics[Sim,"target"]
  if (verbose) cat("\n target:", target)
  
  # compute all possible combination of sets S for the extracted target in the DAG
  S_sets <- obtain_S(target, d)
  
  # extract the true causal parents of the extracted target
  parents <- get_parents(target,dag = dag)
  if (length(parents)==0){
    parents_no <- 0 
  } else {
    parents_no <- unlist( convertSetToNumeric(list(parents)) )
  }
  
  # extract all the accepted sets S from the simulation for the target
  accepted_sets <- get_accepted(pvals[Sim,], S_sets)
  accepted_sets <- convertSetToNumeric(accepted_sets)
  
  # compute the defining set for all accepted Sets of a Simulation
  # def_set <- computeDefiningSets(accepted_sets)
  
  # compute the intersecting set for all accepted Sets of a Simulation
  int_set <- unlist( computeSetIntersection(accepted_sets) )
  if (length(int_set)==0) int_set <- 0 
  
  if (verbose) cat("\n int_set:")
  if (verbose)  print(int_set)
  if (verbose) cat("\n parents_no:")
  if (verbose) print(parents_no)
  
  # Computing the necessary quantities for Jaccard Similarity 
  # hat{S}: defining set (estimate of causal parents)
  # S^*: true causal parents 
  
  # 1) computing |hat{S} ∩ S^*|
  # Intersection with Empty Set:
  # https://proofwiki.org/wiki/Intersection_with_Empty_Set
  
  # 2) computing |hat{S} ∪ S^*|
  # Union with Empty Set:
  # https://proofwiki.org/wiki/Union_with_Empty_Set
  
  
  if (length(parents_no) == 1 && parents_no == 0) {
      if (length(int_set) == 1 && int_set == 0) {
          AbsIntSetVec[Sim] <- AbsUnSetVec[Sim] <- 1
      } else {
          AbsIntSetVec[Sim] <- 0
          AbsUnSetVec[Sim] <- length(int_set)
      }
  } else {
      if (length(int_set) == 1 && int_set == 0) {
          AbsIntSetVec[Sim] <- 0
          AbsUnSetVec[Sim] <- length(parents_no)
      } else {
          AbsIntSetVec[Sim] <- length(computeSetIntersection(list(int_set, parents_no)))
          AbsUnSetVec[Sim] <- length(get_union(list(parents_no, int_set)))
      }
  }
    
  if (verbose) cat("\n AbsIntSetVec[Sim]:")
  if (verbose) print(AbsIntSetVec[Sim])
  if (verbose) cat("\n AbsUnSetVec[Sim]:")
  if (verbose) print(AbsUnSetVec[Sim])
  
  # compute I(S \in S^\star)
  S_in_PA[Sim] <- is_subset(int_set, unlist(append(0, parents_no)) )
}

Jaccard <- AbsIntSetVec/ AbsUnSetVec

statistics <- cbind(statistics, 
                    "AbsIntSetVec" = AbsIntSetVec, 
                    "AbsUnSetVec" = AbsUnSetVec, 
                    "SinPA" = S_in_PA,
                    "Jaccard" = Jaccard)

FWER <- mean(1-S_in_PA); FWER
Jaccard_mean <- mean(Jaccard, na.rm = TRUE); Jaccard_mean
```

# ---------------------------------------------------------------------------- #
# STORE RESULTS
# ---------------------------------------------------------------------------- #


# Customize the methods row number before continuing
```{r}
row_no <- 3
```

# Store FWER and Jaccard Sim. in matrix
```{r}
if (!exists("statsMat")) {
  statsMat <- matrix(NA, 3,2)
  colnames(statsMat) <- c("FWER", "Jaccard_mean"); statsMat
}

statsMat[row_no,1] <- FWER 
statsMat[row_no,2] <- Jaccard_mean 

statsMat
```


# ---------------------------------------------------------------------------- #
# CREATE PLOTS
# ---------------------------------------------------------------------------- #

```{r}
# specify export file name
fig_name <- "JACCARD_FWER_postANM"
# fig_name <- "JACCARD_FWER_preANM"

# Specify export folder
project_folder <- "D:/PAB/Nextcloud/PA/06_UNIGE/master_thesis/icp-engression/"
figure_folder <- "writing/figures/"
figure_dir <- paste(project_folder,figure_folder, sep = "" )

# Open EPS device
postscript(paste(figure_dir, fig_name, ".eps", sep = ""),
           width = 5, height = 5, horizontal = FALSE)  

# Define your data and symbols
x <- statsMat[,1]
y <- statsMat[,2]

# Calculate the range of x and y
x_range <- range(0, 0.3) # range(0, 0.3) 
y_range <- range(0, 1)

# Reduce space around plots
par(mar = c(3, 3, 0.1, 0.1)) # default: par(mar = c(5.1, 4.1, 4.1, 2.1))   

# Create empty plot 
plot(x, y, xlim = x_range, ylim = y_range, type = "n", 
     xlab = "", ylab = "", xaxt = "n", yaxt = "n", bty = "n", ann = FALSE)

# Add axes
axis(1, at = seq(0, 0.3, by = 0.05), labels = sprintf("%.2f", seq(0, 0.3, by = 0.05))) # seq(0, 0.6, by = 0.05)
axis(2, at = seq(0, 1, by = 0.2))

# Add vertical dotted line at x = 0.05
# abline(, lty = 3, ylim = c(0, 1))
segments(0.05, 0, 0.05, 1, lty = 3)

# plotting the observations 
# Point characters: 
# http://www.sthda.com/english/wiki/r-plot-pch-symbols-the-different-point-shapes-available-in-r
  # 1st observation: filled pink square
  points(x[1], y[1], pch = 22, col = "pink", bg = "pink", cex = 2)
  # 2nd observation: green star
  points(x[2], y[2], pch = 2, col = "green", cex = 1.5, lwd=3.4)
  # 2nd observation: green star
  points(x[3], y[3], pch = 11, col = "lightblue", cex = 1.5, lwd=3.4)

# Add legend
legend("topright",
       legend = c("GAM & RDT", "sI-engression & RDT", "sI-engression & QPT"),
       # legend = c("GAM & RDT", "sI-Engression & QPT", "RF & QPT"),
       pch = c(22, 2, 11), 
       col = c("pink", "green", "lightblue"),
       pt.bg = c("pink", "green", "lightblue"), 
       pt.cex = 1,
       cex = 0.8, bty = "n", 
       title = as.expression(bquote(bold("method"))) )


# Add axis labels
mtext("FWER", side = 1, line = 2)
mtext("JACCARD SIMILARITY", side = 2, line = 2)

# Close EPS device
dev.off()  

```



# ------------------------------------------------------------------------------
# Simulation Count


```{r}
statistics <- read.csv("simulation_documentation/postANMs/InvConQuanPred_SimRep_engression.csv", header = TRUE, sep = ";", encoding="UTF-8") 
simIDs <- as.vector(statistics$ID)

statistics <- read.csv("simulation_documentation/postANMs/InvResDisTest_SimRep_engression.csv", header = TRUE, sep = ";", encoding="UTF-8") 
simIDs <- c(simIDs, as.vector(statistics$ID))

statistics <- read.csv("simulation_documentation/postANMs/InvResDisTest_SimRep_GAM.csv", header = TRUE, sep = ";", encoding="UTF-8") 
simIDs <- c(simIDs, as.vector(statistics$ID))
length(unique(simIDs))
```



```{r}
statistics <- read.csv("simulation_documentation/preANMs/InvConQuanPred_preSI_SimRep_RF.csv", header = TRUE, sep = ";", encoding="UTF-8") 
simIDs <- as.vector(statistics$ID)

statistics <- read.csv("simulation_documentation/preANMs/InvConQuanPred_preSI_SimRep_SIengressionQPT.csv", header = TRUE, sep = ";", encoding="UTF-8") 
simIDs <- c(simIDs, as.vector(statistics$ID))

statistics <- read.csv("simulation_documentation/preANMs/InvResDist_SimRep_preSI_GAM.csv", header = TRUE, sep = ";", encoding="UTF-8") 
simIDs <- c(simIDs, as.vector(statistics$ID))
length(unique(simIDs))
```

















