---
title: "Jaccard_FWER_plots"
author: "Philip Boustani"
date: "2024-08-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
# List of required packages
packages <- c(
  "engression",
  "CondIndTests", 
  "lawstat", # For levene.test
  "stats", # For ks.test, wilcox.test
  "mgcv", # for fitting GAMs
  "nonlinearICP",
  "readtext", # loading csv files
  # "utils", # progress bar 
  "foreach",
  "doSNOW",  # parallel processing with progress bar 
  "data.tree", # to create tree structures from hierarchical data
  "quantregForest", # quantile regression forest
  # "InvariantCausalPrediction",
  # "distributionsrd",
  "torch"
)

# First, installing packages which are not yet installed and then loading all of them
load_packages <- function(packages){
  for (pkg in packages) {
    if(!require(pkg, character.only = TRUE)){
      install.packages(pkg, character.only = TRUE);
      library(pkg, character.only = TRUE)
    }
  }
}

# loading packages
load_packages(packages)
```

# load all required source files

```{r}
# List of required source files
files <- c(
)

# if applicable, specify entire folders to be loaded
folders <- c(
  "gaussianEngression",
  "engression_supplementary",
  "external_modified"
)

# Detect working directory and load all files 
load_files <- function(files, folders, directory){
  
  paths <- c(
    file.path(directory, files),
    file.path(directory, list.files(folders, full.names = TRUE))
  )
  
  for (path in paths) {
    source(path)
  }
}

# loading directory  
directory <- getwd()
load_files(files, folders, directory)
```






Baselines: 

  Random:
  random_SimRep_random.csv
  
  linear ICP:
  InvResDist_SimRep_linearICP.csv
  
  nonlinear ICP: 
  Monotone_preSI_QPT_RDT_SimRep_GAM.csv


Methods: 

  fast linear ICE:
  fastSIE_mon_preSI_SimRep_nonmonSIE.csv
  
  flinear ICE
  nonfastSIE_mon_preSI_SimRep_nonmonPredSIE.csv
  
  nonlinear ICE:
  Monotone_preSI_QPT_RDT_SimRep_engression.csv




```{r}
# Monotone_preSI_QPT_RDT_SimRep_engression.csv
statistics <- read.csv("simulations/random_SimRep_random.csv", 
                       header = TRUE, sep = ";", encoding="UTF-8")
statistics <- statistics[statistics$eta_df <=10, ]
statistics <- statistics[statistics$meanshift >=5, ]
pvals <- statistics[ , grepl("pvSet_" , names( statistics ) ) ]
```

```{r}
# Monotone_preSI_QPT_RDT_SimRep_engression.csv
statistics <- read.csv("simulations/InvResDist_SimRep_linearICP.csv", 
                       header = TRUE, sep = ";", encoding="UTF-8")
statistics <- statistics[statistics$eta_df <=10, ]
statistics <- statistics[statistics$meanshift >=5, ]
pvals <- statistics[ , grepl("pvSet_" , names( statistics ) ) ]
```

```{r}
# Monotone_preSI_QPT_RDT_SimRep_engression.csv
statistics <- read.csv("simulations/Monotone_preSI_QPT_RDT_SimRep_GAM.csv", 
                       header = TRUE, sep = ";", encoding="UTF-8")
statistics <- statistics[statistics$eta_df <=10, ]
statistics <- statistics[statistics$meanshift >=5, ]
pvals <- statistics[ , grepl("pvSet_" , names( statistics ) ) ]
```

```{r}
# Monotone_preSI_QPT_RDT_SimRep_engression.csv
statistics <- read.csv("simulations/fastSIE_mon_preSI_SimRep_nonmonSIE.csv", 
                       header = TRUE, sep = ";", encoding="UTF-8")
statistics <- statistics[statistics$eta_df <=10, ]
statistics <- statistics[statistics$meanshift >=5, ]
pvals <- statistics[ , grepl("pvSet_" , names( statistics ) ) ]
```

```{r}
# Monotone_preSI_QPT_RDT_SimRep_engression.csv
statistics <- read.csv("simulations/nonfastSIE_mon_preSI_SimRep_nonmonPredSIE.csv", 
                       header = TRUE, sep = ";", encoding="UTF-8")
statistics <- statistics[statistics$eta_df <=10, ]
statistics <- statistics[statistics$meanshift >=5, ]
pvals <- statistics[ , grepl("pvSet_" , names( statistics ) ) ]
```

```{r}
# Monotone_preSI_QPT_RDT_SimRep_engression.csv
statistics <- read.csv("simulations/Monotone_preSI_QPT_RDT_SimRep_engression.csv", 
                       header = TRUE, sep = ";", encoding="UTF-8")
statistics <- statistics[statistics$eta_df <=10, ]
statistics <- statistics[statistics$meanshift >=5, ]
pvals <- statistics[ , grepl("pvSet_" , names( statistics ) ) ]
```




```{r}
# Define a function to clean and convert the values
clean_numeric <- function(x) {
  x <- gsub(",", ".", x)  # Replace commas with periods
  return(as.numeric(x))   # Convert to numeric
}
pvals <- as.data.frame(lapply(pvals, function(col) sapply(col, clean_numeric)))

# clean data from missing rows
NArows <- which(apply(pvals, 1, function(row) any(is.na(row))))
pvals <- pvals[-NArows,]
statistics <- statistics[-NArows,]
```


```{r}
verbose <- FALSE 
nvec <- nrow(pvals)
AbsIntSetVec <- numeric(nvec)
AbsUnSetVec <- numeric(nvec)
S_in_PA <- numeric(nvec)
int_set_vec <- character(nvec)

for (Sim in 1:nvec) {
  
  if (verbose) cat("\n Sim:",Sim)
  # extract target of the Simulation
  target <- statistics[Sim,"target"]
  if (verbose) cat("\n target:", target)
  
  # compute all possible combination of sets S for the extracted target in the DAG
  S_sets <- obtain_S(target, d)
  
  # extract the true causal parents of the extracted target
  parents <- get_parents(target,dag = dag)
  if (length(parents)==0){
    parents_no <- 0 
  } else {
    parents_no <- unlist( convertSetToNumeric(list(parents)) )
  }
  
  # extract all the accepted sets S from the simulation for the target
  accepted_sets <- get_accepted(pvals[Sim,], S_sets)
  accepted_sets <- convertSetToNumeric(accepted_sets)
  
  # compute the defining set for all accepted Sets of a Simulation
  # def_set <- computeDefiningSets(accepted_sets)
  
  # compute the intersecting set for all accepted Sets of a Simulation
  int_set <- unlist( computeSetIntersection(accepted_sets) )
  if (length(int_set)==0) int_set <- 0 
  
  if (verbose) cat("\n int_set:")
  if (verbose)  print(int_set)
  if (verbose) cat("\n parents_no:")
  if (verbose) print(parents_no)
  
  # Computing the necessary quantities for Jaccard Similarity 
  # hat{S}: defining set (estimate of causal parents)
  # S^*: true causal parents 
  
  # 1) computing |hat{S} ∩ S^*|
  # Intersection with Empty Set:
  # https://proofwiki.org/wiki/Intersection_with_Empty_Set
  
  # 2) computing |hat{S} ∪ S^*|
  # Union with Empty Set:
  # https://proofwiki.org/wiki/Union_with_Empty_Set
  
  
  if (length(parents_no) == 1 && parents_no == 0) {
      if (length(int_set) == 1 && int_set == 0) {
          AbsIntSetVec[Sim] <- AbsUnSetVec[Sim] <- 1
      } else {
          AbsIntSetVec[Sim] <- 0
          AbsUnSetVec[Sim] <- length(int_set)
      }
  } else {
      if (length(int_set) == 1 && int_set == 0) {
          AbsIntSetVec[Sim] <- 0
          AbsUnSetVec[Sim] <- length(parents_no)
      } else {
          AbsIntSetVec[Sim] <- length(computeSetIntersection(list(int_set, parents_no)))
          AbsUnSetVec[Sim] <- length(get_union(list(parents_no, int_set)))
      }
  }
    
  if (verbose) cat("\n AbsIntSetVec[Sim]:")
  if (verbose) print(AbsIntSetVec[Sim])
  if (verbose) cat("\n AbsUnSetVec[Sim]:")
  if (verbose) print(AbsUnSetVec[Sim])
  
  # compute I(S \in S^\star)
  S_in_PA[Sim] <- is_subset(int_set, unlist(append(0, parents_no)) )
}

Jaccard <- AbsIntSetVec/ AbsUnSetVec

statistics <- cbind(statistics, 
                    "AbsIntSetVec" = AbsIntSetVec, 
                    "AbsUnSetVec" = AbsUnSetVec, 
                    "SinPA" = S_in_PA,
                    "Jaccard" = Jaccard)

FWER <- mean(1-S_in_PA); FWER
Jaccard_mean <- mean(Jaccard, na.rm = TRUE); Jaccard_mean
```

# ---------------------------------------------------------------------------- #
# STORE RESULTS
# ---------------------------------------------------------------------------- #


# Customize the methods row number before continuing
```{r}
row_no <- 6
```

# Store FWER and Jaccard Sim. in matrix
```{r}
if (!exists("statsMat")) {
  statsMat <- matrix(NA, 6,2)
  colnames(statsMat) <- c("FWER", "Jaccard_mean"); statsMat
}

statsMat[row_no,1] <- FWER 
statsMat[row_no,2] <- Jaccard_mean 

statsMat
```


# ---------------------------------------------------------------------------- #
# CREATE PLOTS
# ---------------------------------------------------------------------------- #

```{r}
# specify export file name
fig_name <- "JACCARD_FWER_preANM_smalldf"
# fig_name <- "JACCARD_FWER_preANM"

# Specify export folder
project_folder <- "D:/PAB/Nextcloud/PA/06_UNIGE/master_thesis/icp-engression/"
figure_folder <- "writing/figures/"
figure_dir <- paste(project_folder,figure_folder, sep = "" )

# Open EPS device
postscript(paste(figure_dir, fig_name, ".eps", sep = ""),
           width = 5, height = 5, horizontal = FALSE)

# Define your data and symbols
x <- statsMat[,1]
y <- statsMat[,2]

# Calculate the range of x and y
x_range <- seq(0, 0.09, by = 0.01)
y_range <- seq(0.25, 0.45, by = 0.05)

# Reduce space around plots
par(mar = c(3, 3, 0.1, 0.1)) # default: par(mar = c(5.1, 4.1, 4.1, 2.1))   

# Create empty plot 
plot(x, y, xlim = range(x_range), ylim = range(y_range), type = "n", 
     xlab = "", ylab = "", xaxt = "n", yaxt = "n", bty = "n", ann = FALSE)

# Add axes
axis(1, at = x_range) #, labels = sprintf("%.2f", seq(0, 0.3, by = 0.05))) # seq(0, 0.6, by = 0.05)
axis(2, at = y_range)

# Add vertical dotted line at x = 0.05
# abline(, lty = 3, ylim = c(0, 1))
segments(0.05, 0, 0.05, 1, lty = 3)

# plotting the observations 
# Point characters: 
# http://www.sthda.com/english/wiki/r-plot-pch-symbols-the-different-point-shapes-available-in-r

color_vec <- c("pink", "darkseagreen1", "burlywood", "dodgerblue4", "darkorange", "magenta")
pch_vec <- c(22, 2, 11, 12, 8, 4)
  # 1st observation: filled pink square
  points(x[1], y[1], pch = pch_vec[1], col = color_vec[1] , bg = color_vec[1], cex = 2)
  # 2nd observation: green star
  points(x[2], y[2], pch = pch_vec[2], col = color_vec[2], cex = 1.5, lwd=3.4)
  # 2nd observation: green star
  points(x[3], y[3], pch = pch_vec[3], col =color_vec[3] , cex = 1.5, lwd=3.4)
  
  points(x[4], y[4], pch = pch_vec[4], col = color_vec[4], cex = 1.5, lwd=3.4)
  
  points(x[5], y[5], pch = pch_vec[5], col = color_vec[5], cex = 1.5, lwd=3.4)
  
  points(x[6], y[6], pch = pch_vec[6], col = color_vec[6], cex = 1.5, lwd=3.4)

# Add legend
legend("topleft",
       legend = c("random", "linear ICP", "nonlinear ICP", 
                  "fast linear ICE", "linear ICE", "nonlinear ICE"),
       # legend = c("GAM & RDT", "sI-Engression & QPT", "RF & QPT"),
       pch = pch_vec, 
       col = color_vec,
       pt.bg = color_vec, 
       pt.cex = 1,
       cex = 1, bty = "n", 
       title = as.expression(bquote(bold("method"))) )


# Add axis labels
mtext("FWER", side = 1, line = 2)
mtext("JACCARD SIMILARITY", side = 2, line = 2)

# Close EPS device
dev.off()

```